### 2021-06-11 ANA-TOPQ-2019-17-PAPER-metadata.tex
rename fcnc-paper to ANA-TOPQ-2019-17-PAPER

% Title
%\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
\AtlasTitle{Search for top-quark decays $t \to Hq$ with 36 fb$^{-1}$ of $pp$ collision data at $\sqrt{s}=13~\tev$ with the ATLAS detector}

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
%\AtlasVersion{2.2}
% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%
A search for flavour-changing neutral current decays of a top quark into an up-type quark ($q=u, c$) and the 
Standard Model Higgs boson, $t\to Hq$, is presented. 
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
CERN Large Hadron Collider and corresponding to an integrated luminosity of 36.1 fb$^{-1}$.
Two complementary analyses are performed to search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$ decay modes, respectively.  
The high multiplicity of $b$-quark jets, or the presence of hadronically decaying $\tau$-leptons, is exploited in the two analyses respectively. 
Multivariate techniques are used to separate the signal from the background, which is dominated by top-quark pair production.
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
The combination of these searches with ATLAS searches in diphoton and multilepton final states 
%significantly improves the sensitivity, 
yields observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), respectively.
The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
%These are the most restrictive direct bounds on $tqH$ interactions obtained so far.
}

@@

% ATLAS reference code, to help ATLAS members to locate the paper
\AtlasRefCode{TOPQ-2017-07}
%\AtlasRefCode{ATLAS-CONF-2018-049}

@@

% Submission journal and final reference
\AtlasJournal{JHEP}
% \AtlasJournal{Phys.\ Lett.\ B.}
\AtlasJournalRef{JHEP 05 (2019) 123}
\AtlasDOI{10.1007/JHEP05(2019)123}

% CERN preprint number ---> can be found in CDS entry for Draft 2!
\PreprintIdNumber{CERN-EP-2018-295}

@@

% List of supporting notes  (leave as null \AtlasCoverSupportingNote{} if you want to skip this option)
\AtlasCoverSupportingNote{Search for $\ttbar \to WbHq$, $H \to b\bar{b}$}{https://cds.cern.ch/record/2257631}
\AtlasCoverSupportingNote{Search for $\ttbar \to WbHq$, $H \to \tau^+\tau^-$}{https://cds.cern.ch/record/2273683}
\AtlasCoverSupportingNote{Combination of $\ttbar \to WbHq$ searches}{https://cds.cern.ch/record/2312520/}
%
% OR (the 2nd option is deprecated, especially for CONF and PUB notes)
%
% Supporting material TWiki page  (leave as null \AtlasCoverTwikiURL{} if you want to skip this option)
% \AtlasCoverTwikiURL{https://twiki.cern.ch/twiki/bin/view/Atlas/WebHome}

% Comment deadline
\AtlasCoverCommentsDeadline{4 November 2018}

% Analysis team members - contact editors should no longer be specified
% as there is a generic email list name for the editors
\AtlasCoverAnalysisTeam{
$H \to b\bar{b}$: Trisha Farooque, Davide Gerbaudo, Aurelio Juste, Nicola Orlando,  \\ Cheng Peng,  Laura Pereira, 
Yulia Rodina, Yanjun Tu,  Lo\"ic Val\'ery, \\ Tal Van Daalen, Jia-Shian Wang, Daiki Yamaguchi; \\
$H \to \tau^+\tau^-$: Xin Chen, Antonio De Maria, Boyang Li, Ligang Xia, Gang Zhang; \\
Combination: Peter Onyisi, Harish Potti}

% Editorial Board Members - indicate the Chair by a (chair) after his/her name
% Give either all members at once (then they appear on one line), or separately
\AtlasCoverEdBoardMember{Ketevi Assamagan~(chair), Garabed Halladjian, Fabrice Hubaut, Michele Weber~(chair)}

@@

% Editors egroup
\AtlasCoverEgroupEditors{atlas-TOPQ-2017-07-editors@cern.ch}

% EdBoard egroup
\AtlasCoverEgroupEdBoard{atlas-TOPQ-2017-07-editorial-board@cern.ch}

>>>>

% Title
%\AtlasTitle{Search for flavor-changing neutral current $t\rightarrow Hq$ ($q=u,c$) decays in pp collisions at $\sqrt{s}$=13 TeV with the ATLAS detector }
\AtlasTitle{Search for flavour-changing neutral current $tHq$ interections of the top quark and the Higgs boson which decays into a pair of $\tau$-leptons
                   with 139 fb$^{-1}$ of $pp$ collision data at $\sqrt{s}=13~\tev$ with the ATLAS detector}

% Draft version:
% Should be 1.0 for the first circulation, and 2.0 for the second circulation.
% If given, adds draft version on front page, a 'DRAFT' box on top of each other page, 
% and line numbers.
% Comment or remove in final version.
%\AtlasVersion{2.2}
% Abstract - % directly after { is important for correct indentation
\AtlasAbstract{%

A search for flavour-changing neutral current $tHq$ interections with a top quark, an up-type quark ($q=u, c$), and the
Standard Model Higgs boson is presented. The Higgs boson decay to a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the 
CERN Large Hadron Collider and corresponding to an integrated luminosity of 139.6 fb$^{-1}$.
Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in
which one top quark decays into $Wb$ and the other top quark with FCNC decay of $t\rightarrow Hq$. 
The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$),
as well as multiple jets.  
Multivariate techniques are used to separate the signal from the background on the basis of their different kinematics.
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
Observed (expected) 95\% CL upper limits are set on the $t\to Hc$ and $t\to Hu$ branching ratios of XXX ($0.046^{+0.020}_{-0.012}\%$) 
and XXX ($0.034^{+0.014}_{-0.012}\%$), respectively.
%The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
%These are the most restrictive direct bounds on $tqH$ interactions obtained so far.
}

@@

% ATLAS reference code, to help ATLAS members to locate the paper
\AtlasRefCode{TOPQ-2019-17}
%\AtlasRefCode{ATLAS-CONF-2018-049}

@@

% Submission journal and final reference
\AtlasJournal{JHEP}
% \AtlasJournal{Phys.\ Lett.\ B.}
%\AtlasJournalRef{JHEP 05 (2019) 123}
%\AtlasDOI{10.1007/JHEP05(2019)123}

% CERN preprint number ---> can be found in CDS entry for Draft 2!
%\PreprintIdNumber{CERN-EP-2018-295}

@@

% List of supporting notes  (leave as null \AtlasCoverSupportingNote{} if you want to skip this option)
%\AtlasCoverSupportingNote{Search for $\ttbar \to WbHq$, $H \to b\bar{b}$}{https://cds.cern.ch/record/2257631}
%\AtlasCoverSupportingNote{Search for $\ttbar \to WbHq$, $H \to \tau^+\tau^-$}{https://cds.cern.ch/record/2273683}
%\AtlasCoverSupportingNote{Combination of $\ttbar \to WbHq$ searches}{https://cds.cern.ch/record/2312520/}
\AtlasCoverSupportingNote{Search for flavor-changing neutral currents tHq interactions with, $H \to \tau^+\tau^-$}{https://cds.cern.ch/record/2687866}
%
% OR (the 2nd option is deprecated, especially for CONF and PUB notes)
%
% Supporting material TWiki page  (leave as null \AtlasCoverTwikiURL{} if you want to skip this option)
% \AtlasCoverTwikiURL{https://twiki.cern.ch/twiki/bin/view/Atlas/WebHome}

% Comment deadline
\AtlasCoverCommentsDeadline{1 November 2021}

% Analysis team members - contact editors should no longer be specified
% as there is a generic email list name for the editors
\AtlasCoverAnalysisTeam{
Xin Chen, Boyang Li, Mingming Xia, Wei-Ming Yao}
%Combination: Peter Onyisi, Harish Potti}

% Editorial Board Members - indicate the Chair by a (chair) after his/her name
% Give either all members at once (then they appear on one line), or separately
\AtlasCoverEdBoardMember{Not assigned yet!}

@@

% Editors egroup
\AtlasCoverEgroupEditors{atlas-TOPQ-2019-17-editors@cern.ch}

% EdBoard egroup
\AtlasCoverEgroupEdBoard{atlas-TOPQ-2019-17-editorial-board@cern.ch}

### 2021-06-11 sections/conclusion.tex
rename fcnc-paper to ANA-TOPQ-2019-17-PAPER

A search for flavour-changing neutral-current decays of a top quark into an up-type quark ($q=u, c$) and the Standard Model Higgs boson, $t\to Hq$, is presented. 
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded in 2015 and 2016 with the ATLAS detector at the 
CERN Large Hadron Collider and corresponding to an integrated luminosity of 36.1 fb$^{-1}$.
Two complementary analyses are performed to search for top-quark pair events in which one top quark decays into $Wb$ and the other top quark decays into $Hq$,
and target the $H \to b\bar{b}$ and $H \to \tau^+\tau^-$  decay modes, respectively.  
The $\Hbb$ search selects events with one isolated electron or muon from the $W \to \ell\nu$ decay, and multiple jets, with several 
of them being identified with high purity as originating from the hadronisation of $b$-quarks. 
The $\Htautau$ search selects events with either one or two hadronically decaying $\tau$-lepton candidates, as well as multiple jets. 
Both searches employ multivariate techniques to discriminate between the signal and the background on the basis of their different kinematics. 
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
In the case of the $\Hbb$ search, the observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $4.2 \times 10^{-3}\,(4.0 \times 10^{-3})$ and $5.2 \times 10^{-3}\,(4.9 \times 10^{-3})$, respectively.
In the case of the $\Htautau$ search, the observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios 
are $1.9 \times 10^{-3}\,(2.1 \times 10^{-3})$ and $1.7 \times 10^{-3}\,(2.0 \times 10^{-3})$, respectively.
The combination of these searches with ATLAS searches in diphoton and multilepton final states 
%significantly improves the sensitivity, 
yields observed (expected) 95\% CL upper limits on the $t\to Hc$ and $t\to Hu$ branching ratios of $1.1 \times 10^{-3}$ ($8.3 \times 10^{-4}$) 
and $1.2 \times 10^{-3}$ ($8.3 \times 10^{-4}$), assuming $\BR(t\to Hu)=0$ and $\BR(t\to Hc)=0$ respectively.
The corresponding combined observed (expected) upper limits on the $|\lambda_{tcH}|$ and $|\lambda_{tuH}|$ couplings are 0.064 (0.055) and 0.066 (0.055), respectively. 
%Upper limits in the $t\to Hc$ versus $t\to Hu$ branching ratio plane, as well as best-fit branching ratios, are also reported.
These are the most restrictive direct bounds on $tqH$ ($q=u,c$) interactions obtained so far.

>>>>

A search for flavour-changing neutral current $tHq$ interections with a top quark,	an up-type quark ($q=u, c$), and the
Standard Model Higgs boson is presented. The Higgs boson decay to a pair of $\tau$-leptons, $H\rightarrow \tau^+\tau^-$, is considered.
The search is based on a dataset of $pp$ collisions at $\sqrt{s}=13~\tev$ recorded with the ATLAS detector at the
CERN Large Hadron Collider and corresponding to an integrated luminosity of 139.6 fb$^{-1}$.
Two production processes are considered:  single top quark FCNC production in association with the Higgs boson ($pp\rightarrow tH$), and top quark pair production in
which one top quark decays into $Wb$ and the other top quark with FCNC decay of $t\rightarrow Hq$.
The search selects events with two hadronically decaying $\tau$-lepton candidates ($\tauhad$) or at least one $\tauhad$ with an additional lepton(e,$\mu$),
as well as multiple jets.
Multivariate techniques are used to separate the signal from the background on the basis of their different kinematics.
No significant excess of events above the background expectation is found, and 95\% CL upper limits on the $t\to Hq$ branching ratios are derived.
Observed (expected) 95\% CL upper limits are set on the $t\to Hc$ and $t\to Hu$ branching ratios of XXX ($0.046^{+0.020}_{-0.012}\%$)
and XXX ($0.034^{+0.014}_{-0.012}\%$), respectively.
